\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{7}

### 2015-09-14 ICRA2016/bandits_docs/includes/related_work.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

%For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
Considerable research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{li2005shape}.
Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps using the Iterated Closest Point algorithm~\cite{goldfeder2011data}.
Research has also studied transferring grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative}.
%, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics. 
Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
The authors found that the full system of object recognition, pose estimation, and grasp execution successfully grasped objects on a table in 80\% of trials.

Another line of research has focused on synthesizing grasps using statistical models learned from a database of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
%Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a library of prototypical graspable point clouds, and showed that the representation could be transferred to real sensor data~\cite{detry2013learning}.
Lenz et al.~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface rendered along the surface normal.
In comparison, we learn a model to predict a belief distribution on the probability of force closure for a parallel-jaw grasp on a new object based on similarity to prior 3D objects and grasps, and we actively choose the next grasp to evaluate using Multi-Armed Bandits.

Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{salganicoff1996active}.
%Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net to further accelerate convergence to a grasp with high probability of force closure.

% DEEP LEARNING
To use the prior information contained in our database on a new model, we also draw on past research on 3D model similarity.
One can separate the methods to compare 3D shapes in roughly two categories.
On one side, some methods encode the geometric characteristics of the shape, such as its curvature or characteristics of the harmonic functions on the shape~\cite{horn1984extended, kazhdan2003rotation, bronstein2011shape}. 
hese methods mainly rely on the use of hand-design descriptors, with the notable exception of~\cite{wu20153d} which learn a CNN on the voxel representation of the shape.
On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{murase1995visual,chen2003visual}.
One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented consistently.
The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating them with second CNN which learns the invariance to orientation.
Using this method, the authors improve state of the art classification results on ModelNet40 by a large margin.
In a different set up, a simpler average pooling of the features from different views was proposed in~\cite{aubry2015understanding}.
We use a similar strategy by max-pooling the features, which we found to perform better than average pooling.

>>>>

Robust grasp planning considers the problem of finding a set of grasps for an object that may succeed over perturbations in object shape,  object pose, and environment configurations due to uncertainty resulting from imprecision in perception and control.
Research on grasp planning for precisely known objects and environments has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS)~\cite{ferrari1992, liu2015fast}.
The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{li2005shape}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
This led to research on methods for transferring grasps from objects in databases, such as warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control.
%, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} found that grasps ranked by probability of force closure or Ferrari-Canny quality subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
Hsiao et al.~\cite{hsiao2011bayesian} developed a Bayesian framework for grasp success on physical robot under uncertainty in object shape, object pose, and robot control and used GraspIt! to estimate the probability of success on a database of 892 point clouds of 3D objects.
%Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
The authors found that the full system of object recognition, pose estimation, and grasp execution successfully grasped objects on a table in 80\% of trials.

Another line of research has focused on synthesizing grasps using statistical models learned from a databse of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning} of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
%Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
%Much research in this area has been concerned with learning a set of grasp affordance features from images~\cite{lenz2015deep, saxena2008robotic} or point clouds~\cite{detry2013learning, herzog2014learning}.
Herzog et al.~\cite{herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
In comparison, we learn a model that predicts a belief distribution on the probability of force closure for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and we demonstrate that the predicted belief can be used to reduce the number samples needed to plan a robust grasp with Multi-Armed Bandits.

Our work is also closely related to research on actively sampling grasps to build a predictive model of grasp quality from fewer examples~\cite{detry2011learning, kehoe2012estimating, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
However, their approach does not incorporate prior knowledge.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based Multi-Armed Bandit (MAB) algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high probability of force closure.

% DEEP LEARNING
To use the prior information contained in our database on a new model, we also draw on past research on 3D model similarity.
One line of past research has focused on encoding geometric characteristics of a shape, such as its curvature, characteristics of the harmonic functions on the shape~\cite{bronstein2011shape, horn1984extended, kazhdan2003rotation}, or using CNNs trained on a voxel representation of shapes~\cite{maturana2015voxnet, wu20153d}.
On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented consistently.
The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating the views with a second CNN that learns the invariance to orientation.
Using this method, the authors improve state-of-the-art classification accuracy on ModelNet40 by 10\%.
We use a max-pooling to aggregate views, inspired by recent results using axerage pooling~\cite{aubry2015understanding} proposed a simpler average pooling of the features from different views.

### 2015-09-14 ICRA2016/bandits_docs/paper.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale
%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{6}}
\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,3}$, \\
Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^2$
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{$^3$ Universite Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
\thanks{$^4$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
\TODO{Convert figures to pdfs} \\
\TODO{Trim paper to 8 pages} \\
\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}

@@

\section{Acknowledgments}
This research was performed with UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.

>>>>

\usepackage[switch, columnwise]{lineno}
\linenumbers

@@

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale
%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{7}}
\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,3}$, \\
Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^{1,2}$
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{$^3$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
\thanks{$^4$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
\TODO{Trim paper to 8 pages} \\
\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}

@@

\section{Acknowledgments}
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
